\subsection{Frano Cavelis}
	\paragraph{Education}
		\begin{itemize}
			\item 2012 - Present: RIT Croatia - Information Technology
			\item 2008 - 2012: Tourism and Hospitality school Dubrovnik - Hotel and Tourism
		\end{itemize}
	\paragraph{Work Experience}
		\begin{itemize}
			\item RIT Croatia - IT support \hfill Summer 2015\\
			Offered professional IT support to all staff and faculty members, prepared classrooms and private rooms for meetings, operated the Polycom system, helped new IT and IHSM candidates during boot camp, assisted newly arrived professors at the campus, reorganized technical equipment through the campus, installed new network devices, was involved in several marketing projects
			\item RIT Croatia - Student Helper \hfill Fall 2014\\
			Made sure the labs were organized and operational, helped students, staff and professor with relevant information, intervened with technical failures, moved the Polycom to different classrooms where he is needed and set it up, relocated other technical equipment, attended presentations and events for technical support, worked at the reception, filmed videos for the RIT Croatia marketing department on multiple locations, created multimedia on a professors request
			\item RIT Croatia - IT Support \hfill Summer 2014\\
			Helped the staff, professors and students with technical and other issues, set up and maintaining classrooms, labs and the Polycom, gathered information on current technical inventory and procuring reports on technical equipment, browsed for new equipment to possibly order, reformatted and installed new software
			\item Hotel Bellevue - Waiter \hfill Summer 2013\\
			Served a large number of hotel guests, carried and cleaned equipment, operated a cashier, delivered food item to guests' rooms
		\end{itemize}
	\paragraph{Software Skills}
	
		\begin{itemize}
			\item Java, C\#, XHTML
			\item HTML, CSS, JavaScript
			\item jQuery, PHP
		\end{itemize}

\subsection{Andrew Wood}
	\paragraph{Education}
		\begin{itemize}
			\item RIT - Information Technology, Minor in Human Communications
		\end{itemize}
	\paragraph{Work Experience}
		\begin{itemize}
			\item RIT - Web Developer \hfill May 2014 - Dec 2014\\
			Designed, developed and implemented a web platform along with administrative tools for the Interactive Games and Media department at RIT. Developed a system of dynamic document generation to automate time consuming tasks. Developed a logging system of company inventory to keep track of crucial workplace items. Heavy influence in the design of a database that supported essential tasks and stored vital company information.
		\end{itemize}
	\paragraph{Software Skills}
		\begin{itemize}
			\item Java, C\#, Python, Objective-C
			\item Heavy SQL experience
			\item PHP, JavaScript, jQuery, AJAX
			\item HTML, CSS, NodeJS, Cordova
			\item PhoneGap, Android SDK 
		\end{itemize}
	
\subsection{Tomomi Takeuchi}
	\paragraph{Education}
		\begin{itemize}
			\item RIT - Information Technology
			\item Sophia University - CIEE Arts and Science Study Abroad
		\end{itemize}
	\paragraph{Work Experience}
		\begin{itemize}
			\item Japanese Voice-Over \hfill Fall 2015\\
			Voiced over a presentation and tutorial video in Japanese for a new medical equipment line
			\item Japanese Teacher \hfill Spring 2015\\
			Built and taught a personalized curriculum corresponding to students' level of Japanese
			\item Application Development Engineer Assitant \hfill Winter 2014\\
			Supervised debugging team and revised interfaces and JavaScript code before submission. Created application content using Adobe Photoshop, Illustrator, Flash and InDesign. Compiled completed components using XML
			\item Application/Website Developer \hfill Summer 2014\\
			Developed an education mathematics application for elementary level children. Inputted and edited data using various Adobe software. Built website interface with support of Adobe Dreamweaver.
			\item Homepage Designer \hfill Summer 2013\\
			Designed and implemented a multi-page website in HTML and CSS
			\item Research Assistant \hfill Spring 2013\\
			Recruited test subject candidates through social media and on-campus. Proctored computer based Japanese tests for data-collection. Provided technical support with testing software and collected data files
		\end{itemize}
	\paragraph{Software Skills}
		\begin{itemize}
			\item Java, C\#, HTML, CSS, MySQL
			\item JavaScript, jQuery, PHP, XML
		\end{itemize}

\subsection{Daniel Dorrity}
	\paragraph{Education}
		\begin{itemize}
			\item RIT - Information Technology, Minor in Mathematics
		\end{itemize}
	\paragraph{Work Experience}
		\begin{itemize}
			\item RIT Student IT Office \hfill June 2015 - Present\\
			Team lead and technical project manager. Tasked with gathering technical requirements and determining risks and benefits of multiple solutions at a single time. Project manager for a team consisting of multiple members of RIT ITS. In charge of leading meetings and making sure required work is done on time. 
			\item RIT Student IT Office \hfill Jan. 2015 - June 2015\\
			Web developer tasked with programming features for student enrollment application. Full stack development, ranging from Java Spring back end development, to AngularJS front end development. Small amounts of HTML and CSS modifications. 
			\item RIT Corner Store \hfill Sept. 2013 - Dec. 2014\\
			Student manager in charge of making sure students are doing their assigned tasks. In charge of the store and any major decisions while supervisors are away from the building.
		\end{itemize}
	\paragraph{Software Skills}
		\begin{itemize}
			\item HTML, CSS, JavaScript, AngularJS, Grunt
			\item Gulp, Gradle, Ionic, Swift, MySQL
			\item Java, C\#, Python, UML, LaTeX
		\end{itemize}
